Improving \textsl{Gaia} parallax precision \\ with a data-driven model of stars

### 2017-06-06 paper/paper.tex
Added footnote about deconvolution

In detail, we take the $5\%$
quantile of each parallax posterior (the closest part) and query the 3D dust map at that distance.
We take the $5\%$ quantile---as apposed to the median---to do a minimal dust
correction because over-correcting for dust can push the likelihood
function into an unphysical, extremely blue part of the \cmd\ and thus bias the
parallax inference. At the 3D position of each star, we sample the \texttt{mode=median} value of the probabilistic dust map.
We apply each dust correction to our
\tmass\ photometry using Equation~\ref{eq:data}, where $Q_{\lambda}
= [0.709, 0.302]$ for bands $[J, K_s]$ respectively (see Table 6 in
\citealt{schlafly11}).
The dust values we obtain in our final
iteration, and which we apply to the photometry in our inference, are visualized in
galactic coordinates in \figurename~\ref{fig:dust}.
After applying the dust correction, we do not update the uncertainties, which is
technically wrong and under-represents the true uncertainties; this leads to a less severe deconvolution, as mentioned previously.
In other words, the features of our inferred
  \cmd\ are conservatively broad (broader than if we over-estimated
  the errors which would have lead to excessive deconvolution and
  unrealistically narrow features). We could add the covariance of
the dust to our likelihoods, but this is beyond the scope of this
demonstration of concept.
\begin{figure}
\centering
  \includegraphics[width=\textwidth]{dust.png}
\caption{The converged dust values at the 5\% distance quantile in Galactic coordinates. This shows both the footprint of our analysis as well as the adopted extinction values. Each point represents a single star in our cross-matched catalog. The large missing areas are due to the \psone\ footprint ($>-30~{\rm deg}$ in declination)}
\label{fig:dust}
\end{figure}

>>>>

In detail, we take the $5\%$
quantile of each parallax posterior (the closest part) and query the 3D dust map at that distance.
We take the $5\%$ quantile---as apposed to the median---to do a minimal dust
correction because over-correcting for dust can push the likelihood
function into an unphysical, extremely blue part of the \cmd\ and thus bias the
parallax inference. At the 3D position of each star, we sample the \texttt{mode=median} value of the probabilistic dust map.
We apply each dust correction to our
\tmass\ photometry using Equation~\ref{eq:data}, where $Q_{\lambda}
= [0.709, 0.302]$ for bands $[J, K_s]$ respectively (see Table 6 in
\citealt{schlafly11}).
The dust values we obtain in our final
iteration, and which we apply to the photometry in our inference, are visualized in
galactic coordinates in \figurename~\ref{fig:dust}.
After applying the dust correction, we do not update the uncertainties, which is
technically wrong and under-represents the true uncertainties; this leads to a less severe deconvolution, as mentioned previously.
In other words, the features of our inferred
  \cmd\ are conservatively broad\footnote{This can be understood by considering the following procedure: if one incrementally increase the noise levels (leaving the data unchanged; just increasing the declared uncertainties), the deconvolved distribution will be increasingly narrower, since it targets the distribution that would generate the noiseless observations, as well as the observed data once noise is added}. We could add the covariance of
the dust to our likelihoods, but this is beyond the scope of this
demonstration of concept.
\begin{figure}
\centering
  \includegraphics[width=\textwidth]{dust.png}
\caption{The converged dust values at the 5\% distance quantile in Galactic coordinates. This shows both the footprint of our analysis as well as the adopted extinction values. Each point represents a single star in our cross-matched catalog. The large missing areas are due to the \psone\ footprint ($>-30~{\rm deg}$ in declination)}
\label{fig:dust}
\end{figure}
